An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-27 draft.tex
Minor corrections

Figure \ref{fig:experiment_flow} shows the workflow users can follow to run
experiments in Evo\-Swarm. The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm Developers can upload the container definition or images directly to
DockerHub. Another option is to upload the image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the Docker compose file to specify the
type and number of containers needed for the application.  The Docker compose
application is responsible for starting all the containers or downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script using the
experiment id to generate a collection of files containing all the data
generated by the experiment. The script generates these files in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper.  There is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.

@@

To test the heterogeneous multi-population capabilities,  we compare the
performance between a homogeneous and an ensemble of multi-populations, using
Genetic Algorithms (GAs) and Particle Swarm Optimization (PSO). For the GA
implementation, we used the DEAP library \cite{fortin2012deap} and for the  PSO,
the EvoloPy library \cite{faris2016evolopy}. Both Python libraries are
open-source. In EvoSwarm these two algorithms are implemented as stateless
functions.

Next, we show the parameters for each algorithm, in Table \ref{tab:GAparams} 
for the GA and in Table \ref{tab:PSOparams} for PSO. We obtained these parameters 
following the same method as in a previous work \cite{garcia2017benchmarking}. 
To obtain the parameters, we tested first on the
Rastrigin separable function with five dimensions. After about fifteen
experiments, the most challenging targets were achieved for this particular
function. We tested again with functions one to three, and after obtaining
favorable results, the PSO and GA algorithm parameters were set.In the GA, we
randomly set the mutation and crossover probabilities to have more
heterogeneous workers; in these parameters, the range of values is specified.

>>>>

Figure \ref{fig:experiment_flow} shows the workflow users can follow to run
experiments in Evo\-Swarm. The first step is to develop the search strategy
algorithms that are going to be used by the multi-population algorithm.
Algorithm developers can upload the container definition or images directly to
DockerHub. Another option is to upload the image definition (Dockerfile) to
GitHub and define a trigger to re-upload the image to DockerHub.  Docker Compose
configuration files can reference these containers. When a user needs to deploy
the application, he or she needs to edit the {\tt docker-compose.yml} file to specify the
type and number of containers needed for the application.  The {\tt docker-compose}
application is responsible for starting all the containers or downloading new
versions if it is necessary. After starting the application, users can push
Experiment Definition files and start monitoring the execution in the terminal.
After the experiment is finished, the user must execute another script using the
experiment id to generate a collection of files containing all the data
generated by the experiment. The script generates these files in a JSON format.
Researchers can use these files to analyze and plot experiment data.  Python
scripts are included in the repository to plot the running times for the
experiments, and all other plots used in this paper.  There is also a script to
generate the files needed by the COCO framework \cite{hansen2016coco}, which can generate standard
comparisons against other methods.

@@

To test the heterogeneous multi-population capabilities,  we compare the
performance between a homogeneous and an ensemble of multi-populations, using
Genetic Algorithms (GAs) and Particle Swarm Optimization (PSO). For the GA
implementation, we used the DEAP library \cite{fortin2012deap} and for the  PSO,
the EvoloPy library \cite{faris2016evolopy}. Both Python libraries are
open-source. In EvoSwarm these two algorithms are implemented as stateless
functions. % Did you release this also with a free license? Point to
           % the URL - JJ

Next, we show the parameters for each algorithm, in Table \ref{tab:GAparams} 
for the GA and in Table \ref{tab:PSOparams} for PSO. We obtained these parameters 
following the same method as in a previous work \cite{garcia2017benchmarking}. 
To obtain the parameters, we tested first on the
Rastrigin separable function with five dimensions. After about fifteen
experiments, the most challenging targets were achieved for this particular
function. We tested again with functions one to three, and after obtaining
favorable results, the PSO and GA algorithm parameters were set. In the GA, we
randomly set the mutation and crossover probabilities to have more
heterogeneous workers; in these parameters, the range of values is specified.
